Lens Modeling in \sw

### 2013-09-10 text/tex/results.tex
labels
some figure changes

@@

Figure \ref{fig:6971} shows incorrect identification, but the enclosed
mass still quite well recovered.

@@

The assignment of the parity of the images (T1b) posed a more difficult task.
In 59\% (R2, p=0.59, N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to E06, with N=38, p=32\%, followed by E05 (PI) with N=7, p=6\%.
For an example of E06, see \figref{6971}, it basically describes a situation, where the minima and saddlepoints were exchanged (rotated by $\pm90\dgr$).
E05 describes the situation, where the ordering of the saddle points was wrong (rotation by $180\dgr$)
While these errors occurred, we suspect they can be avoided with better training material and some examples for the obvious cases.
For more challenging cases, like very symmetrical distribution of the lensed images (for example model 6971, \figref{6971}), those errors should still produce plausible results, as will be explained in the next section.

\subsection{Second test T2} \label{sec:results.2}

>>>>

Figure \ref{fig:7022} shows incorrect identification, but the enclosed
mass still quite well recovered.

@@

@@

The assignment of the parity of the images (T1b) posed a more difficult task.
In 59\% (R2, p=0.59, N=70) of the cases the volunteers succeeded to identify the right configuration.
Most of the failures are due to E06, with N=38, p=32\%, followed by E05 (PI) with N=7, p=6\%.
For an example of E06, see \figref{7022}, it basically describes a situation, where the minima and saddlepoints were exchanged (rotated by $\pm90\dgr$).
E05 describes the situation, where the ordering of the saddle points was wrong (rotation by $180\dgr$)
While these errors occurred, we suspect they can be avoided with better training material and some examples for the obvious cases.
For more challenging cases, like very symmetrical distribution of the lensed images (for example model 7022, \figref{7022}), those errors should still produce plausible results, as will be explained in the next section.

\subsection{Second test T2} \label{sec:tests.t2}
